%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.52in,right=0.75in,bottom=0.52in]{geometry} % Document margins
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{marvosym}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,      
    urlcolor=cyan,
}
 
\urlstyle{same}

\name{Palash Nigam}
\address{\href{https://palash25.netlify.com/}{palash25.netlify.com/} \\
         \href{mailto:npalash25@gmail.com}{npalash25@gmail.com}\ \\
         \href{https://www.linkedin.com/in/palash25}{in/palash25} \\
         \href{https://github.com/palash25}{github.com/palash25}
         \color{black}{+91-7394092346}}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
  \begin{rSummarySection}
  {
    \item Experience with backend web services and open source development. Interested in distributed systems and infrastructure.
    \item Go, Python, Rust, Ruby, Erlang, Elixir; Git, ElasticSearch, MongoDB, Redis
  }
  \end{rSummarySection}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
  \begin{rWorkSection}{Hackerrank}
                      {Bangalore, India}
                      {SDE Intern}
                      {Jan '20 -- Present}
  {
    \item Wrote a git analytics engine from scratch in Go that extracts data from hundreds of repos concurrently and derives meaningful insights from it.
    \item Wrote the rails backend for the git dashboard's webapp and designed the Elasticsearch schema for it.
    \item Adding support for language runtimes like Rust, SBCL, etc for Hackerrank's code execution service called Coderunner
  }
  \end{rWorkSection}
  \begin{rWorkSection}{Cloud Native Computing Foundation}
                      {Remote}
                      {Community Bridge Intern}
                      {Jul -- Aug '19}
  {
    \item Wrote a \href{https://github.com/coredns/coredns/pull/3011}{plugin} to serve DNS records from Google Cloud DNS to coredns.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Atlan}
                     {New Delhi, India}
                     {Software Development Intern (Backend)}
                     {May -- Jun '19}
  {
    \item Rewrote \href{https://collect.atlan.com/}{Collect}'s Analytics API (originally in Python) in Go and deployed it on GCP.
    \item Ported parts of the Collect monolith from NodeJS to Go.
    \item Proof of Concept on improving Collect's ElasticSearch cluster topology.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Appbase}
                     {Remote}
                     {Software Engineering Intern}
                     {Sep '18 -- Jul '19}
  {
    \item Wrote an adaptor to sync data between Redis and Elasticsearch for a data ingestion pipeline named \href{http://github.com/appbaseio/abc/}{abc} in Go.
    \item Implemented cluster management and analytics support for \href{http://github.com/appbaseio/abc/}{abc}.
    \item Wrote unit and integration tests for an \href{https://github.com/appbaseio/arc}{Elasticsearch API Gateway}
  }
  \end{rWorkSection}
  
  \begin{rWorkSection}{coala Association e.V.}
                     {Remote}
                     {Google Summer of Code Student}
                     {May -- Aug '18}
  {
    \item Improved \href{http://coala.io/}{coala}'s I/O mechanism by implementing FileFactory - an abstraction layer to interface with files and enable lazy loading.
    \item Integrated FileFactory with coala's old core by implementing a middleware thereby ensuring backwards compatibility and enabling furhter enhancement of the Nextgen Core.
    \item Wrote a Persistent Hash module for generating unique hashes for coala's task objects to improve the cache accuracy.
  }
  \end{rWorkSection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
  \begin{rProjectSection}
    \item \textbf {wc-rs} -- \href{https://github.com/palash25/wc-rs}{\underline{Rust port}} of the wc unix command. \underline{2.5X faster} than GNU wc
    \item \textbf {foaas-cli} -- \href{https://github.com/palash25/foaas-cli}{\underline{CLI tool}} for FOaaS API with 100\texttt{+} stars on Github
    \item \textbf {unirest-go} -- Kong's Unirest protocol \href{https://github.com/palash25/unirest-go}{\underline{implemented in Go}}
  \end{rProjectSection}

  \begin{rBlurbSection}
    \item {\em Open-source contributions:}
      \href{http://bit.ly/2LfMLIW}{\textbf{google/go-github}},
      \href{http://bit.ly/2Quw26G}{\textbf{coala}},
      \href{http://bit.ly/2NLmHsD}{\textbf{ethereum}},
      \href{https://github.com/coredns/coredns/pull/3011}{\textbf{coredns}} and
      \href{http://bit.ly/2lJ4PCy}{\textbf{various others}}
  \end{rBlurbSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteer Experience}
  \begin{tabular}{rll}
2018	     & {\href{http://bit.ly/2OsNuqI}{Github Campus Expert}}  & Introducing OSS development in my campus.\\
2018	     & Google Code In Mentor  & Mentored High School students in OSS development.\\
2018	     & Programming Society Head  & Led the college programming club.\\
\end{tabular}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rEducationSection}{International Institute of Information Technology, Bhubaneswar}
                           {Aug '16 -- Jul '20}
                           {Bachelors of Technology in Computer Science and Engineering \space \space \space \space \space\space \space \space\space \space \space\space \space \space\space \space \space\space \space \space\space Grade: 6.9}
  \end{rEducationSection}
\end{rSection}

\end{document}
